Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-08-01 msbr_reproc.tex

This analysis models a single representative unit cell rather than the whole 
\gls{MSBR} core. Consequently, it does not take into consideration different 
fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
initial multiplication factor during depletion calculation is selected for 
state with fully withdrawn control and poison rods position which gives 
considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
Standard deviation for these calculations is approximately 100 pcm.

@@

These results are contrary with those of Jeong and Park (2016) who suggested 
two different unit cell models and uses \gls{MCNP} with Python-script to 
simulate \gls{MSBR} online reprocessing to find equilibrium composition. This 
inconsistency may be due to different fuel fraction in the unit cell (Jeong and 
Park selected 20.6\% salt fraction). To obtain better results for this online 
reprocessing simulation, many future efforts are planned. First, a depletion 
simulation will be performed using a  full-core, three-dimensional, high-fidelity 
model of \gls{MSBR} that has been developed in Serpent 2. In this case, different 
fuel-moderator volume ratios for the reactor Zone I, Zone II, annulus, 
reflectors would be taken into account to find accurate multiplication factor, 
neutron spectrum and, hence, depleted composition. Secondly, additional Serpent 
2 flow control system subroutine should be developed to simulate adjusting 
material flows (e.g. rate of removing $^{233}$Pa from the salt and adding 
fissile $^{233}$U from the tank for protactinium decay) depending upon current 
reactivity value which is more promising reactivity control method than moving 
control and safety rods. Finally, temperature effect of reactivity for both 
fuel salt and graphite should be calculated to find optimal effective 
multiplication factor range.

>>>>

This analysis models a single representative unit cell rather than the whole 
\gls{MSBR} core. Consequently, it does not take into consideration different 
fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
initial multiplication factor during depletion calculation is selected for 
a state with fully withdrawn control rods, which gives 
considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
Standard deviation for these calculations is approximately 100 pcm.

@@

These results are contrary with those of Jeong and Park (2016) who suggested 
two different unit cell models and uses \gls{MCNP} with Python-script to 
simulate \gls{MSBR} online reprocessing to find equilibrium composition. This 
inconsistency may be due to different fuel fraction in the unit cell (Jeong and 
Park selected 20.6\% salt fraction). To obtain better results for this online 
reprocessing simulation, many future efforts are planned. First, a depletion 
simulation will be performed using a  full-core, three-dimensional, high-fidelity 
model of \gls{MSBR} that has been developed in Serpent 2. In this case, different 
fuel-moderator volume ratios for the reactor Zone I, Zone II, annulus, 
and reflectors will be taken into account to find accurate multiplication factor, 
neutron spectrum and, hence, depleted composition. Secondly, an additional Serpent 
2 flow control system subroutine should be developed to simulate adjusting 
material flows (e.g. rate of removing $^{233}$Pa from the salt and adding 
fissile $^{233}$U from the tank for protactinium decay) depending upon the 
instantaneous reactivity value, which is a more promising reactivity control method than moving 
control rods. Finally, the temperature effect of reactivity for both 
fuel salt and graphite should be calculated to find optimal effective 
multiplication factor range.
